Efficient and Scalable Bayesian Bipartite Matching through Fast Beta Linkage (\texttt{fabl})

### 2021-11-15 Prelim/prelim.tex
NLTCS case study

\documentclass{beamer}
\usetheme{Rochester}
\addtobeamertemplate{navigation symbols}{}{ \hspace{1em}    \usebeamerfont{footline}%
	\insertframenumber / \inserttotalframenumber }
\begin{document}
	\title{Efficient and Scalable Bipartite Matching through Fast Beta Linkage (fabl)}
	%\subtitle{Using Beamer}
	\author{Brian Kundinger, Jerome Reiter, Rebecca Steorts}
	\institute{Duke University}
	\date{\today}

@@

		\item Far ranging applications in business, public health, and human rights
	\end{enumerate}
	\end{frame}

\begin{frame}{Record Linkage in Practice}
	\begin{columns}
		\begin{column}{0.48\textwidth}
			\includegraphics<1->[width = \textwidth, height = 1.2\textwidth ]{ted_article2.png}

		\end{column}
		\begin{column}{0.48\textwidth}
			\includegraphics<2->[width = \textwidth, height = 1.2\textwidth ]{dnc_header.png}
		\end{column}
	\end{columns}
\end{frame}

	\begin{frame}{Linkage for Downstream Analysis}
	\includegraphics<1>[width = \textwidth, height = .7\textwidth ]{datasets.png}
	\includegraphics<2>[width = \textwidth, height = .7\textwidth ]{datasets_linked.png}

\end{frame}

	\begin{frame}{Linkage through Comparison Vectors}
		\includegraphics[width = \textwidth, height = .7\textwidth ]{fs_graphic.png}
	\end{frame}

\begin{frame}{Fellegi and Sunter (1969)}
	\begin{columns}
		\begin{column}{0.6\textwidth}
			\includegraphics<1>[width = \textwidth, height = 1.2\textwidth ]{rl_graphics_all/Slide1.png}
			\includegraphics<2->[width = \textwidth, height = 1.2\textwidth ]{rl_graphics_all/Slide2.png}

		\end{column}
		\begin{column}{0.38\textwidth}
			\begin{itemize}
				\item<3-> scalable to large datasets (\texttt{fastlink}, Enamorado et al 2017)
				\item<4-> no transitive closure, requires post-processing
				\pause 
				\item<5-> overmatches, leading to inaccurate parameter estimation
			\end{itemize}

@@

\begin{frame}{Sadinle (2017) - Beta Record Linkage}
	\begin{columns}
		\begin{column}{0.6\textwidth}
			\includegraphics<1>[width = \textwidth, height = 1.2\textwidth ]{rl_graphics_all/Slide1.png}
			\includegraphics<2>[width = \textwidth, height = 1.2\textwidth ]{rl_graphics_all/Slide3.png}
			\includegraphics<3>[width = \textwidth, height = 1.2\textwidth ]{rl_graphics_all/Slide4.png}
			\includegraphics<4->[width = \textwidth, height = 1.2\textwidth ]{rl_graphics_all/Slide5.png}

		\end{column}
		\begin{column}{0.38\textwidth}
			\begin{itemize}
				\item<1-> Beta Record Linkage (\texttt{BRL})
				\pause
				\item<5-> strictly enforces one-to-one matching, no post-processing
				\pause
				\item<6-> high accuracy for linkage and other parameters
				\pause 
				\item<7-> inherently serial, not scalable to large linkage tasks
			\end{itemize}

@@

\begin{frame}{Our Contribution - Fast Beta Linkage}
	\begin{columns}
		\begin{column}{0.6\textwidth}
			\includegraphics<1>[width = \textwidth, height = 1.2\textwidth ]{rl_graphics_all/Slide1.png}
			\includegraphics<2->[width = \textwidth, height = 1.2\textwidth ]{rl_graphics_all/Slide6.png}

		\end{column}
		\begin{column}{0.38\textwidth}
			\begin{itemize}
				\item<3-> simple mathematical change, large computational gains
				\item<4-> minimal loss of accuracy for linkage and other parameters, minimal post-processing
			\end{itemize}

@@

\section{Fast Beta Linkage}
\begin{frame}{Notation}
\begin{itemize}
	\item File A with records indexed $i \in \{1, \ldots, n_A\}$ and file B with records $j \in \{1, \ldots, n_B\}$. We use $F$ features for linkage, with $L_f$ possible levels of agreement on feature $f$.

	\item $\Gamma \in \mathbb{R}^{n_A n_B \times F}$ matrix of comparison vectors where $\gamma_{ij}^f \in \{1, \ldots, L_f\}$

	\item $Z_j = \begin{cases} 
	i,  & \text{if records } i\in A \text{ and } j\in B \text{ match}; \\
	n_A + 1,  & \text{if record } j\in B \text{ has no match in } A; \\
	\end{cases}$

	\item $m_{fl} = P\left(\gamma_{ij}^f = l |Z_j = i\right)$

	\item $u_{fl} = P\left(\gamma_{ij}^f = l |Z_j \neq i\right)$

	\item $\lambda = P(Z_j \leq n_A)$
\end{itemize}
\end{frame}

\begin{frame}{Fast Beta Linkage (fabl)}
	$$P(\Gamma|\mathbf{Z}, \mathbf{m}, \mathbf{u}) = \prod_{j=1}^{n_B}  \prod_{i=1}^{n_A}\left[ \prod_{f=1}^{F}\prod_{l=1}^{L_f} m_{fl}^{I(Z_j = i)}u_{fl}^{I(Z_j \neq i)}\right]^{I(\gamma_{ij}^f = l)}$$

	$$\mathbf{m_{f}} \sim \text{Dirichlet}(\alpha_{f1}, \ldots, \alpha_{fL_f})$$
	$$\mathbf{u_{f}} \sim \text{Dirichlet}(\beta_{f1}, \ldots, \beta_{fL_f})$$
	$$Z_j | \lambda =
	\begin{cases} 
	\frac{1}{n_A}\lambda  & z_j \leq n_A; \\
	1-\lambda &  z_j  = n_A + 1 \\
	\end{cases}$$
	$$\lambda \sim \text{Beta}(\alpha_{\lambda}, \beta_{\lambda})$$

	Model specification allows for \textbf{parallel/distributed} computing, \textbf{hashing} of comparison vectors, and \textbf{storage efficient indexing (SEI)}
\end{frame}

\begin{frame}{Hashing}
	\begin{itemize}
		\item Recognize there are at most $P = \prod_{f = 1}^F L_f$ unique agreement patterns, regardless of number of records. When $(i,j)$ pair exhibits agreement pattern $p$, say $h(i, j)=p.$

		\item Reduce data to sufficient statistics
		\begin{itemize}
		\item $r_{p_j} = \{i \;|\, (i, j) \in h_p\}$
		\item $H_{p_j} = ||r_{p_j}||$
		\item $H_p = \sum_{j} H_{p_j}$
		\end{itemize}

		\item Run Gibbs sampler at level of agreement patterns, not record pairs
		\begin{itemize}
		\item Sample the agreement of pattern $h(z_j, j)$, instead of record label $z_j$.
		\item Use number of matches for each pattern to update $m$ and $u$
		\item Back fill record labels at the end through $r_{p_j}$
	\end{itemize}

		\item Reduces computational complexity from $O(n_A \times n_B \times F)$ to $O(P \times n_B \times F)$
	\end{itemize}
\end{frame}

\begin{frame}{Managing Large Data}
	\begin{itemize}
		\item \textbf{Distributed Computing} - Partition data in to chunks $\{A_I\}$ and $\{B_J\}$. Compare records, hash results, compute summary statistics in parallel, and synthesize results.

		\item \textbf{Storage Efficient Indexing (SEI)} - Store at most small number $R$ many record labels in each $r_{p_j}$, remove highly unlikely record labels from memory. Proper weights for calculations maintained through summary statistics $\{H_p\}$ and $\{H_{p_j}\}$.

		\item Hashing plus SEI can reduce memory requirements by >99%
		\begin{itemize}
			\item Simulation of $20,000 \times 20,000$ linkage task with 4 fields. Naive approach requires 6.4GB of storage for all-to-all comparisons, hashing and SEI requires 90MB.
		\end{itemize}
	\end{itemize}
\end{frame}

\section{Results}

\begin{frame}{Three Simulation Studies}
	\begin{itemize}
		\item We compare \texttt{fabl} against \texttt{BRL} in three simulation studies
		\begin{itemize}
			\item Measure precision and recall on 100 simulated datasets and varying levels of error and duplication across files
			\item Measure speed when both $n_A$ and $n_B$ are increasing
			\item Measure speed when $n_A$ is increasing and $n_B = 500$ is fixed. 
		\end{itemize}
	\end{itemize}
\end{frame}

	\begin{frame}{Accuracy Simulation}
	\includegraphics[width = \textwidth, height = .7\textwidth ]{../notes/figures/sadinle_sim_plot.png}
\end{frame}

	\begin{frame}{Speed Simulation 1}
	\includegraphics[width = \textwidth, height = .7\textwidth ]{../notes/figures/sadinle_speed_plot2.png}
\end{frame}

	\begin{frame}{Speed Simulation 2}
	\includegraphics[width = \textwidth, height = .7\textwidth ]{../notes/figures/speed_plot_fixed_nB.png}
\end{frame}

\begin{frame}{Extensions and Directions}
	\begin{itemize}
	\item Linkage in the face of duplicates within datasets

	\item Models that allow reliability of information to differ by subgroup in the data

@@

>>>>

\documentclass{beamer}
\usetheme{Rochester}
\addtobeamertemplate{navigation symbols}{}{ \hspace{1em}    \usebeamerfont{footline}%
	\insertframenumber / \inserttotalframenumber }
\begin{document}
	\title{Efficient and Scalable Bayesian Bipartite Matching through Fast Beta Linkage (\texttt{fabl})}
	%\subtitle{Using Beamer}
	\author{Brian Kundinger, Jerome Reiter, Rebecca Steorts}
	\institute{Duke University}
	\date{\today}

@@

		\item \textbf{Bipartite matching} is the specific goal of matching one record in one dataset to most one match in another dataset
	\end{itemize}
	\end{frame}

%\begin{frame}{Record Linkage in Practice}
%	\begin{columns}
%		\begin{column}{0.48\textwidth}
%			\includegraphics<1->[width = \textwidth, height = .9\textwidth ]{ted_article2.png}
%			
%		\end{column}
%		\begin{column}{0.48\textwidth}
%			\includegraphics<2->[width = \textwidth, height = .9\textwidth ]{dnc_header.png}
%		\end{column}
%	\end{columns}
%\end{frame}

\begin{frame}{Record Linkage in Practice}
	\centering
	\includegraphics<1->[width = .8\textwidth, height = .6\textwidth ]{graphics/syria_article_big.png}
\end{frame}

\begin{frame}{Record Linkage in Practice}
	\includegraphics<1->[width = \textwidth, height = .6\textwidth ]{graphics/dnc_big.png}
\end{frame}

\begin{frame}{Linkage for Downstream Analysis}
	\includegraphics<1>[width = \textwidth, height = .7\textwidth ]{graphics/Slide1.png}
	\includegraphics<2>[width = \textwidth, height = .7\textwidth ]{graphics/Slide2.png}
\end{frame}

\begin{frame}{Linkage through Comparison Vectors}
	\includegraphics<1>[width = \textwidth, height = .6\textwidth ]{graphics/Slide3.png}
	\includegraphics<2>[width = \textwidth, height = .6\textwidth ]{graphics/Slide4.png}
	\includegraphics<3>[width = \textwidth, height = .6\textwidth ]{graphics/Slide5.png}
\end{frame}

\begin{frame}{Linkage through Comparison Vectors}
	Represent linkage structure through vector $\mathbf{Z} = \{Z_1, \ldots, Z_{n_B}\}$, where
\begin{center}
	$Z_j = \begin{cases} 
		i,  & \text{if records } i\in A \text{ and } j\in B \text{ match}; \\
		n_A + 1,  & \text{if record } j\in B \text{ has no match in } A; \\
	\end{cases}$
\end{center}
\end{frame}

\begin{frame}{Linkage through Comparison Vectors}
	\includegraphics[width = \textwidth, height = .6\textwidth ]{graphics/Slide6.png}
\end{frame}

\begin{frame}{Fellegi and Sunter (1969)}
	\begin{columns}
		\begin{column}{0.6\textwidth}
			\includegraphics<1>[width = \textwidth, height = 1.2\textwidth ]{graphics_square/Slide1.png}
			\includegraphics<2->[width = \textwidth, height = 1.2\textwidth ]{graphics_square/Slide2.png}
		\end{column}
		\begin{column}{0.38\textwidth}
			\begin{itemize}
				\item<3-> scalable to large datasets (\texttt{fastlink}, Enamorado et al 2019)
				\item<4-> not bipartite, requires post-processing
				\pause 
				\item<5-> overmatches, leading to inaccurate parameter estimation
			\end{itemize}

@@

\begin{frame}{Sadinle (2017)}
	\begin{columns}
		\begin{column}{0.6\textwidth}
			\includegraphics<1>[width = \textwidth, height = 1.2\textwidth ]{graphics_square/Slide1.png}
			\includegraphics<2>[width = \textwidth, height = 1.2\textwidth ]{graphics_square/Slide3.png}
			\includegraphics<3>[width = \textwidth, height = 1.2\textwidth ]{graphics_square/Slide4.png}
			\includegraphics<4->[width = \textwidth, height = 1.2\textwidth ]{graphics_square/Slide5.png}
		\end{column}
		\begin{column}{0.38\textwidth}
			\begin{itemize}
				\item<1-> Beta Record Linkage (\texttt{BRL})
				\pause
				\item<5-> strictly enforces one-to-one matching, no post-processing
				\pause
				\item<6-> high accuracy for linkage and other parameters
				\pause 
				\item<7-> inherently serial, not scalable to large linkage tasks
			\end{itemize}

@@

\begin{frame}{Our Contribution - Fast Beta Linkage}
	\begin{columns}
		\begin{column}{0.6\textwidth}
			\includegraphics<1>[width = \textwidth, height = 1.2\textwidth ]{graphics_square/Slide1.png}
			\includegraphics<2-4>[width = \textwidth, height = 1.2\textwidth ]{graphics_square/Slide6.png}
			\includegraphics<5>[width = \textwidth, height = 1.2\textwidth ]{graphics_square/Slide7.png}
			\includegraphics<6>[width = \textwidth, height = 1.2\textwidth ]{graphics_square/Slide8.png}
		\end{column}
		\begin{column}{0.38\textwidth}
			\begin{itemize}
				\item<3-> relaxation proposed by Heck Wortman (2019)
				\item<4-> minimal loss of accuracy, large computational gains
				\item<5-> allows for "one to many" matchings
				\item<6-> simple postprocessing to obtain bipartite matching
			\end{itemize}

@@

\section{Fast Beta Linkage}
%\begin{frame}{Notation}
%\begin{itemize}
%	\item File A with records indexed $i \in \{1, \ldots, n_A\}$ and file B with records $j \in \{1, \ldots, n_B\}$, with $n_A \geq n_B$. We use $F$ features for linkage, with $L_f$ possible levels of agreement on feature $f$.
%	
%	\item $\Gamma \in \mathbb{R}^{n_A n_B \times F}$ matrix of comparison vectors where $\gamma_{ij}^f \in \{1, \ldots, L_f\}$
%	
%	\item $Z_j = \begin{cases} 
%	i,  & \text{if records } i\in A \text{ and } j\in B \text{ match}; \\
%	n_A + 1,  & \text{if record } j\in B \text{ has no match in } A; \\
%	\end{cases}$
%	
%	\item $m_{fl} = P\left(\gamma_{ij}^f = l |Z_j = i\right)$
%	
%	\item $u_{fl} = P\left(\gamma_{ij}^f = l |Z_j \neq i\right)$
%	
%	\item $\lambda = P(Z_j \leq n_A)$
%\end{itemize}
%\end{frame}

\begin{frame}{Fast Beta Linkage (\texttt{fabl})}
	$$P(\Gamma|\mathbf{Z}, \mathbf{m}, \mathbf{u}) = \prod_{j=1}^{n_B}  \prod_{i=1}^{n_A}\left[ \prod_{f=1}^{F}\prod_{l=1}^{L_f} m_{fl}^{I(Z_j = i)}u_{fl}^{I(Z_j \neq i)}\right]^{I(\gamma_{ij}^f = l)}$$

	$$\mathbf{m_{f}} \sim \text{Dirichlet}(\alpha_{f1}, \ldots, \alpha_{fL_f})$$
	$$\mathbf{u_{f}} \sim \text{Dirichlet}(\beta_{f1}, \ldots, \beta_{fL_f})$$
	$$Z_j | \pi	\begin{cases} 
	\frac{\pi}{n_A}  & z_j \leq n_A; \\
	1-\pi &  z_j  = n_A + 1 \\
	\end{cases}$$
	$$\pi \sim \text{Beta}(\alpha_{\pi}, \beta_{\pi})$$

	Model specification allows for \textbf{hashing} of comparison vectors, \textbf{distributed} computing, and \textbf{storage efficient indexing (SEI)}
\end{frame}

\begin{frame}{Hashing}
		\begin{columns}
		\begin{column}{0.6\textwidth}
			\begin{itemize}
				\item<1-> Recognize there are at most $P = \prod_{f = 1}^F L_f$ unique agreement patterns, regardless of number of records (Enamorado et al 2019).
				\begin{itemize}
					\item<2-> $L = \{3, 3, 2, 2\}$ implies 36 unique patterns 
				\end{itemize} 
				\item<3-> When $(i,j)$ pair exhibits agreement pattern $p$, say $(i, j) \in h_p.$
				\item<4-> Allows us to compute sufficient statistics and reduce computational complexity from $O(n_A \times n_B)$ to $O(P \times n_B)$
			\end{itemize}
		\end{column}
		\begin{column}{0.38\textwidth}
			\includegraphics<2->[width = \textwidth, height = 1.2\textwidth ]{graphics/unique_patterns.png}
		\end{column}
	\end{columns}
\end{frame}

\begin{frame}{Hashing}
	\centering
	\includegraphics<1>[width = 1.1\textwidth, height = .6\textwidth ]{graphics/Slide17.png}
	\includegraphics<2>[width = 1.1\textwidth, height = .6\textwidth ]{graphics/Slide18.png}
	\includegraphics<3>[width = 1.1\textwidth, height = .6\textwidth ]{graphics/Slide19.png}
	\includegraphics<4>[width = 1.1\textwidth, height = .6\textwidth ]{graphics/Slide20.png}
	\includegraphics<5>[width = 1.1\textwidth, height = .6\textwidth ]{graphics/Slide21.png}	
\end{frame}

\begin{frame}{Hashing to Scale to Large Linkage Tasks}
	\includegraphics<1>[width = \textwidth, height = .6\textwidth ]{graphics/Slide23.png}
	\includegraphics<2>[width = \textwidth, height = .6\textwidth ]{graphics/Slide24.png}
	\includegraphics<3>[width = \textwidth, height = .6\textwidth ]{graphics/Slide25.png}
	\includegraphics<4>[width = \textwidth, height = .6\textwidth ]{graphics/Slide26.png}
	\includegraphics<5>[width = \textwidth, height = .6\textwidth ]{graphics/Slide27.png}
\end{frame}

\begin{frame}{Hashing for Speed (Efficient Gibbs Sampling)}
	\includegraphics<1>[width = \textwidth, height = .6\textwidth ]{graphics/Slide37.png}
	\includegraphics<2>[width = \textwidth, height = .6\textwidth ]{graphics/Slide38.png}
	\includegraphics<3>[width = \textwidth, height = .6\textwidth ]{graphics/Slide39.png}
	\includegraphics<4>[width = \textwidth, height = .6\textwidth ]{graphics/Slide40.png}
	\includegraphics<5>[width = \textwidth, height = .6\textwidth ]{graphics/Slide41.png}
	\includegraphics<6>[width = \textwidth, height = .6\textwidth ]{graphics/Slide42.png}
\end{frame}

%\begin{frame}{Managing Large Data}
%	\begin{itemize}
%		\item \textbf{Distributed Computing} - Partition data in to chunks $\{A_I\}$ and $\{B_J\}$. Compare records, hash results, compute summary statistics in parallel, and synthesize results.
%		
%		\item \textbf{Storage Efficient Indexing (SEI)} - Store at most small number $R$ many record labels in each $r_{p_j}$, remove highly unlikely record labels from memory. Proper weights for calculations maintained through summary statistics $\{H_p\}$ and $\{H_{p_j}\}$.
%		
%		\item Hashing plus SEI can reduce memory requirements by $>99$.
%		\begin{itemize}
%			\item Simulation of $20,000 \times 20,000$ linkage task with 4 fields. Naive approach requires 6.4GB of storage for all-to-all comparisons, hashing and SEI requires 90MB.
%		\end{itemize}
%	\end{itemize}
%\end{frame}

\section{Simulation Studies}

%\begin{frame}{Three Simulation Studies}
%	\begin{itemize}
%		\item We compare \texttt{fabl} against \texttt{BRL} in three simulation studies
%		\begin{itemize}
%			\item Measure precision and recall on 100 simulated datasets and varying levels of error and duplication across files
%			\item Measure speed when both $n_A$ and $n_B$ are increasing
%			\item Measure speed when $n_A$ is increasing and $n_B = 500$ is fixed. 
%		\end{itemize}
%	\end{itemize}
%\end{frame}

\begin{frame}{Speed Simulation 1}
	\begin{columns}
		\begin{column}{0.38\textwidth}
			\begin{itemize}
				\item $F$ = 5 comparison fields
				\item L = \{2, 2, 2, 2, 2\}, all binary comparisons
				\item 32 possible patterns
				\item Increase both $n_A$ and $n_B$
			\end{itemize}
		\end{column}
		\begin{column}{0.58\textwidth}
			\includegraphics[width = \textwidth, height = \textwidth ]{../notes/figures/sadinle_speed_plot_slides.png}
		\end{column}
	\end{columns}
\end{frame}

\begin{frame}{Speed Simulation 2}
	\begin{columns}
		\begin{column}{0.38\textwidth}
			\begin{itemize}
				\item $F$ = 5 comparison fields
				\item L = \{2, 2, 2, 2, 2\}, all binary comparisons
				\item 32 possible patterns
				\item Fix $n_B = 500$, increase $n_A$
			\end{itemize}
		\end{column}
		\begin{column}{0.58\textwidth}
			\includegraphics[width = \textwidth, height = \textwidth ]{../notes/figures/speed_plot_fixed_nB_slides.png}
		\end{column}
	\end{columns}
\end{frame}

\begin{frame}{Accuracy Simulation}
	\begin{itemize}
		\item Sadinle (2017) used 900 simulated linkage tasks to show accuracy of \texttt{BRL}
		\item Find matches across two datasets, each with 500 records and 4 fields in common. 
		\item One, two or three errors across matching records
		\item 10\% matching, 50\% matching, or 90\% matching
		\item Calculate recall, precision, and F-measure 
	\end{itemize}
\end{frame}

\begin{frame}{Accuracy Simulation}
	\includegraphics[width = \textwidth, height = .7\textwidth ]{../notes/figures/sadinle_sim_plot2.png}
\end{frame}

%\begin{frame}{Speed Simulation 1}
%	\includegraphics[width = \textwidth, height = .7\textwidth ]{../notes/figures/sadinle_speed_plot2.png}
%\end{frame}
%
%	\begin{frame}{Speed Simulation 2}
%	\includegraphics[width = \textwidth, height = .7\textwidth ]{../notes/figures/speed_plot_fixed_nB.png}
%\end{frame}

%\section{El Salvador Homicide Case Study}
%
%\begin{frame}{El Salvador Case Study}
%	\begin{itemize}
%		\item El Salvadoran Civil War (1980-1991)
%		\item Lists of casualties collected by multiple organizations
%		\begin{itemize}
%			\item Salvadoran Human Rights Commissions (CDHES), $n_A = 4420$
%			\item El Rescate - Tutela Regal (ERTL), $n_B = 1323$
%			\item Features include first name, last name, date and place of death
%		\end{itemize}
%		\item We aim to find duplicate records across files
%		\begin{itemize}
%			\item Particularly difficult because families are often killed together, and some children share names with parents
%		\end{itemize}
%
%	\end{itemize}
%\end{frame}
%
%\begin{frame}{Run Time}
%		\begin{columns}
%		\begin{column}{0.48\textwidth}
%			\centering
%			\includegraphics<1->[width = .6\textwidth, height = .6\textwidth ]{../notes/figures/el_salvador/time_table_big_P2.png}
%			
%		\end{column}
%		\begin{column}{0.48\textwidth}
%			\centering
%			\includegraphics<2>[width = .6\textwidth, height = .6\textwidth ]{../notes/figures/el_salvador/time_table_small_P2.png}	
%		\end{column}
%	\end{columns}
%\end{frame}
%
%\begin{frame}{Posterior Inference}
%	\includegraphics[width = \textwidth, height = .6\textwidth ]{../notes/figures/el_salvador/m_posterior_smallP.png}
%\end{frame}
%
%\begin{frame}{Posterior Inference}
%	\includegraphics[width = \textwidth, height = .6\textwidth ]{../notes/figures/el_salvador/DID_distribution_smallP_bayes.png}
%\end{frame}
%
%\begin{frame}{Violations of One-to-One Matching}
%	\centering
%	\includegraphics[width = .9\textwidth, height = .4\textwidth ]{../notes/figures/el_salvador/rosa_records.png}
%\end{frame}
%
%\begin{frame}{Violations of One-to-One Matching}
%	\includegraphics[width = \textwidth, height = .6\textwidth ]{../notes/figures/el_salvador/bad_mixing.png}
%\end{frame}
%

\section{Conclusion}

\begin{frame}{Benefits of \texttt{fabl}}
	\begin{itemize}
		\item Faster computation for larger linkage tasks

		\item Accurate estimation of linkage structure $\mathbf{Z}$, and additional parameters $\mathbf{m}$ and $\mathbf{u}$

		\item Bayesian model with natural uncertainty quantification
	\end{itemize}
\end{frame}

\begin{frame}{Extensions and Future Directions}
	\begin{itemize}
		\item Linkage when reliability of information and rates of matching differs by subgroup in the data

		\item Linkage when there are duplicates within datasets

@@

\section{Appendix}

\begin{frame}{Storage Efficient Indexing}
	\begin{itemize}
		\item Storing $n_A \times n_B$ hashed values burdensome for large tasks
		\item Overwhelming majority of record pairs show nonagreement
		\item<3> Correct counts for calculations stored in $\mathcal{H}$
	\end{itemize}
	\includegraphics<1>[width = \textwidth]{graphics/before_SEI.png}
	\includegraphics<2->[width = \textwidth]{graphics/after_SEI2.png}
\end{frame}

%		\item Reduce data to sufficient statistics
%		\begin{itemize}
%		\item $r_{p_j} = \{i \;|\, (i, j) \in h_p\}$
%		\item $H_{p_j} = ||r_{p_j}||$
%		\item $H_p = \sum_{j} H_{p_j}$
%		\end{itemize}
%		
%		\item Run Gibbs sampler at level of agreement patterns, not record pairs
%		\begin{itemize}
%		\item Sample the agreement of pattern $h(z_j, j)$, instead of record label $z_j$.
%		\item Use number of matches for each pattern to update $m$ and $u$
%		\item Back fill record labels at the end through $r_{p_j}$
%	\end{itemize}
%
%		\item Reduces computational complexity from $O(n_A \times n_B \times F)$ to $O(P \times n_B \times F)$
